|

### 2021-12-06 text/ManuscriptDraft.Rmd
Manuscript updates (methods)

@@

>>>>

As winds shift, flowers close to the edge of the image .. may move in and out of view. If a flower reappears in the same area as a flower is already being tracked after disappearing in a few frames, it is a reasonable assumption that it is the same individual and not that the old flower wilted/disappeared and a new one developed. The parameter **max disappeared** sets the number of frames a track can be lost before a new track is initiated for points appearing in the same area.

Similarly, this deals with potential false negatives. If a given flower has not been annotated in a single frame, it should not be assigned a new track.

Setting **max disappeared** to 0 tracks objects based on the coordinates of the points in the previous frame.

@@

**Figure 1:** Figure text....
